On The Impact of Atoms of Confusion in JavaScript Code

### 2021-04-20 1_Introduction.tex
additional review of the Introduction

To understand whether an atom of confusion introduces misunderstandings,
we surveyed 140 JavaScript developers. In the survey, 
their task was to predict the output of short code
snippets, with half of them containing atoms of confusion. 
\castor{Improvement of 15\% in terms of what. This is too loose.}
       {\color{red}The number of correct answers for the
         cleaned version of the code snippets for seven (out of nine)
         atom candidates is at least 15\% higher, in comparison to the version
         of the code with the atoms. The presence of an atom candidate
       might also affects the time necessary for submitting a correct answer.}
       For instance, the presence of the Comma Operator atom increases
       the average time to predict the output by 65\%, though the output of snippets containing
       the Pre-Increment atom were correctly predicted 44\% faster.
       To learn more about the misunderstandings in the snippets used in the survey, we interviewed 15
       experienced professional developers. Participants preferred code snippets \textit{without} an atom in 70\% of the cases,
       therefore corroborating with the survey findings. The participants also discussed additional 
       idioms that might lead developers to incorrectly comprehend the JavaScript code.
       The occurrence of atoms in open-source repositories may reveal cases where developers
       should be more or less careful when writing code. To identify such cases, we mined popular JavaScript projects
       from GitHub and found that four atoms are highly used in JavaScript
       code: the Implicit Predicate atom, for instance, occurs 19.89 times per KLOC of
       code.

>>>>

To understand whether an atom of confusion introduces misunderstandings,
we surveyed 140 JavaScript developers. In the survey, 
their task was to predict the output of short code
snippets, with half of them containing atoms of confusion. 
{\color{red}The number of correct answers for the
  \emph{cleaned version} of the code snippets for seven (out of nine)
  atom candidates is at least 15\% higher than the corresponding
  \emph{confuse version
  of the code snippet (i.e., with an atom candidate). The presence of an atom candidate
  might also affects the time necessary for submitting a correct answer.}
  For instance, the presence of the Comma Operator atom increases
  the average time to predict the output by 65\%, though the output of snippets containing
  the Pre-Increment atom were correctly predicted 44\% faster.

  To learn more about the misunderstandings in the snippets used in the survey, we interviewed 15
  experienced professional developers. Participants considered the code snippets without
  the atom candidates easier to understand in 70\% of the cases,
  therefore corroborating the survey findings. The participants also discussed other 
  idioms that might lead developers to misunderstand JavaScript code.
  The occurrence of atoms in open-source repositories might reveal cases where developers
  should be more or less careful when writing code---and open the possibility to implement
  new program transformations for cleaning up confuse code. To identify such cases, we mined popular JavaScript projects
  from GitHub and found four atom candidates that are highly used in JavaScript
  code: the Implicit Predicate atom, for instance, occurs 19.89 times per KLOC of
  code.}
